Supplementary Material for _A Guide to Pre-processing High-Frequency Animal Tracking Data_

### 2021-05-19 supplement/06_bat_data.Rmd
inset fig for concept fig

```{r echo=FALSE}
# now plot over raw data
fig_bat_filter_cov <-
  ggplot() +
  geom_point(
    data = data[!data_split,
      on = c("TAG", "X", "Y", "TIME")
    ],
    aes(X, Y),
    col = "grey",
    shape = 4
  ) +
  geom_path(
    data = data_split,
    aes(X, Y,
      col = TAG
    ),
    show.legend = FALSE
  ) +
  scale_colour_brewer(palette = "Dark2") +
  ggspatial::annotation_scale(location = "br") +
  ggthemes::theme_few() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  ) +
  coord_sf(
    crs = 2039,
    xlim = range(data_split$X),
    ylim = range(data_split$Y)
  )
```

@@

```{r echo=FALSE}
# now plot over raw data
fig_bat_filter_speed <-
  ggplot() +
  geom_path(
    data = data,
    aes(X, Y, group = TAG),
    col = "black",
    size = 0.3
  ) +
  geom_path(
    data = data_split,
    aes(X, Y,
      col = TAG
    ),
    # col = "grey20",
    # size = 0.3,
    show.legend = FALSE
  ) +
  scale_colour_brewer(palette = "Dark2") +
  ggspatial::annotation_scale(location = "br") +
  ggthemes::theme_few() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  ) +
  coord_sf(
    crs = 2039,
    xlim = range(data_split$X),
    ylim = range(data_split$Y)
  )
```

>>>>

```{r echo=FALSE}
# now plot over raw data
# fig_bat_filter_cov <-
  ggplot() +
  geom_point(
    data = data[!data_split,
      on = c("TAG", "X", "Y", "TIME")
    ],
    aes(X, Y),
    col = "grey",
    shape = 4
  ) +
  geom_path(
    data = data_split,
    aes(X, Y,
      col = TAG
    ),
    show.legend = FALSE
  ) +
  scale_colour_brewer(palette = "Dark2") +
  ggspatial::annotation_scale(location = "br") +
  ggthemes::theme_few() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  ) +
  coord_sf(
    crs = 2039,
    xlim = range(data_split$X),
    ylim = range(data_split$Y)
  )
```

@@

```{r echo=FALSE}
# now plot over raw data
fig_bat_filter_speed <-
  ggplot() +
  geom_path(
    data = data,
    aes(X, Y, group = TAG, col = TAG),
    show.legend = F
  ) +
  scale_colour_brewer(palette = "Dark2") +
  ggspatial::annotation_scale(location = "br") +
  ggthemes::theme_few() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  ) +
  coord_sf(
    crs = 2039,
    xlim = range(data_split$X),
    ylim = range(data_split$Y)
  )
```
